\documentclass[12pt]{article}

  % Get right packages
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{amsthm}
  \usepackage{float}
  \usepackage{fullpage} % Package to use full page
  \usepackage{graphicx}
  \usepackage{hyperref}
  \usepackage{parskip} % Package to tweak paragraph skipping

  % User commands
  \newtheorem{thm}{Theorem}
  \DeclareMathOperator*{\argmax}{argmax}

  % Title info
  \title{Taxation Notes}
  \author{UMA Project}
  \date{\today}

\begin{document}

\maketitle

\clearpage
\newpage


\section{Non-technical Summary}

  The UMA Data Verification Machine (DVM) is responsible for producing ``honest'' prices that can be
  used to evaluate financial smart contracts on the blockchain. The DVM relies on votes by
  individuals who own UMA vote tokens to accurately report prices from the fiat world. In order to
  ensure that the DVM cannot be manipulated for financial gain, we must prove that it is
  economically not profitable to corrupt the system by purchasing enough tokens to corrupt the DVM
  by voting dishonestly.

  The tool we use to incentivize honest behavior is to tax the margin held in the financial smart
  contracts and use this margin to conduct buybacks of the UMA vote tokens. We view these buybacks
  as a way to ensure that there are returns paid to holding vote tokens and we prevent corruption
  by ensuring that the expected present discounted value of all future buybacks exceeds the amount
  that an individual could gain by corrupting the system. We build a mathematical model that
  describes these interactions and lay out the conditions necessary to ensure that there is no
  economically profitable corruption opportunities.

  We find that

  \begin{enumerate}
    \item The executed buybacks at high levels of margin are typically higher than buybacks at lower
          levels of margin.
    \item The expectation of growth in margin secured by the DVM coupled with the previous finding
          means that at low levels of margin, the system can be secured simply through the promise
          of future buybacks. Depending on margin growth beliefs and realizations of margin growth,
          this results in the system being secured for a significant period of time (10+ years)
          without actually being required to implement buybacks.
    \item Finding 2
    \item Finding 3
  \end{enumerate}

  These findings motivate our proposed taxation structure

  \clearpage
  \newpage

\section{Technical Details}

  We now move on to describe the technical details of our findings.

  The core of argument will revolve around what we call the ``Profit from Corruption (PfC) less than
  Cost of Corruption (CoC)'' inequality ($PfC < CoC$). This inequality is meant to ensure that no
  one can profitably corrupt the DVM. We assume that the PfC is proportional to the amount of margin
  that is held in the system, $\text{PfC} = \gamma M_t$, and that the CoC is equal to buying
  sufficient vote tokens to corrupt the system\footnote{There are other types of attacks in which
  individuals can offer bribes to individual voters in order to incentivize them to corrupt the
  system --- We have other work in which we can show that the cheapest attack on our system involves
  a 51\% attack}, $\text{CoC} = \chi p_t S_t$ where $p_t$ denotes the dollar price of the UMA vote
  tokens and $S_t$ denotes the outstanding volume of tokens. We also rely on the assumption that
  market prices are accurate --- Namely that if $X_t$ are the dollar amounts of buybacks in each
  period $t$ and $r$ is the interest rate, then the market cap of the token would be
  $p_t S_t = E_t \left[ \sum_{s=0}^{\infty} \left(\frac{1}{1 + r}\right)^s X_t \right]$. Our
  standard assumption will be that the amount of margin that can be stolen is $\frac{1}{2}$ and the
  number of tokens required to corrupt is $\frac{1}{2}$.

  In each of the following subsections, we will use the notation presented below

  \begin{itemize}
    \item $B_t$ denotes the number of tokens bought back prior to vote
    \item $D_t$ denotes the dollar value of funds held in the ``rainy day fund''
    \item $M_t$ denotes total dollar value of margin in system
    \item $\tau_t$ denotes the tax rate on the system
    \item $p_t$ denotes the price (in dollars) of a single vote token
    \item $S_t$ denotes the number of vote tokens outstanding
    \item $T_t \equiv \tau_t M_t$ denotes total tax levied on system
    \item $X_t \equiv B_t p_t$ denotes the dollar value of expenditure on buybacks
  \end{itemize}

  Additionally the following are parameters

  \begin{itemize}
    \item $\chi$ is the fraction of voters required to corrupt the system
    \item $\eta$ is percent of people who do not vote
    \item $\gamma$ the fraction of margin seized if DVM is corrupted
    \item $\pi$ is the inflation rate used to reward voters
    \item $r$ is the risk-free return on other investments
  \end{itemize}

  We can expand and rearrange the $PfC < CoC$ inequality to express the price needed to secure the
  system.

  \begin{align*}
    PfC_t &\leq CoC_t \\
    &\Rightarrow \gamma M_t \leq \frac{1 - \eta}{2} p_t S_t \\
    &\Rightarrow p_t \geq \frac{2}{1 - \eta} \frac{\gamma M_t}{S_t}
    &\Rightarrow p_t \geq \frac{2}{1 - \eta} \frac{\gamma M_t}{S_t}
  \end{align*}

  Thus as long as the price of a token is higher than $\frac{2}{1 - \eta} \frac{\gamma M_t}{S_t}$,
  then it is not profitable to corrupt the system.

  The remaining analysis is done in pieces. We start with the simplest possible model and slowly
  add additional features to deepen our insights. We briefly describe these sections:

  \begin{itemize}
    \item Section \ref{sec:dss} asks the question, ``In a deterministic world in which the system
          margin has reached a steady level of margin, what is the lowest tax rate we can implement
          that ensure incorruptibility?'' We find that the lowest tax rate achievable is the same
          as the return that we would like the tokens to offer.
    \item Section \ref{sec:dg} asks the question, ``If we knew exactly how margin would grow
          in the future, what is the minimum amount of taxes that we could impose at each
          period while maintaining the $PfC < CoC$ guarantee?'' We find that the rate of change in
          the tax rates is similar to the rate of change of the margin held in the system. We find
          that, under a particular parameterization, we can achieve a zero tax rate for almost 20
          years before being required to increase taxes to steady state amounts.
    \item Section \ref{sec:sm} analyzes a model in which margin follows a stationary stochastic
          process and thinks about the right way to smooth taxes while making sure that payments
          can be made to ensure system is incorruptible.''
  \end{itemize}

  \subsection{Deterministic Steady State} \label{sec:dss}
    \input{./TaxationPlanSections/DSS.tex}

  \subsection{Determisitic Growth} \label{sec:dg}
    \input{./TaxationPlanSections/DG.tex}

  \subsection{Stochastic Markov} \label{sec:sm}
    \input{./TaxationPlanSections/SM.tex}

\appendix

\section{Negative Buybacks} \label{app:nbb}
  \input{./TaxationPlanSections/app_negative_buybacks.tex}

\section{Discrete Markov Approximation to Logistic Growth} \label{app:dmc}
  \input{./TaxationPlanSections/app_dmc_approx.tex}

\end{document}
